TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-06 paper/draft.tex
description of data sec

This paper is organized as follows: in Section \ref{sec:data} we describe the technical specifications of the data from the APOGEE survey, as well as our sample selection and derivation of training parameters. 
Section \ref{sec:cannon} describes our model implementation using \thecannon framework.
In Section \ref{sec:results} we present our experimental results, evaluate the predictive accuracy of our models, apply our model to a selected test sample of $>10,000$ sources, and examine the validity of our parameters against color-temperature relations and isochrone grids.
Finally, in Section \ref{sec:discussion} we discuss model performance, future improvements, and implications of our results in the context of present/upcoming stellar and exoplanet surveys.

>>>>

This paper is organized as follows: in Section \ref{sec:data} we describe the technical specifications of the data from the APOGEE survey and previous studies of M dwarfs in APOGEE, as well as our sample selection and derivation of training parameters. 
Section \ref{sec:cannon} describes our model implementation using \thecannon framework.
In Section \ref{sec:results} we present our experimental results, evaluate the predictive accuracy of our models, apply our model to a selected test sample of $>10,000$ sources, and examine the validity of our parameters against color-temperature relations and isochrone grids.
Finally, in Section \ref{sec:discussion} we discuss model performance, future improvements, and implications of our results in the context of present/upcoming stellar and exoplanet surveys.
